\documentclass{letter}
\usepackage{newcent}
\usepackage{hyperref}
\topmargin=-0.5625in
\textheight=9in
\oddsidemargin=-0.0625in
\textwidth=6.5in

%\hyphenpenalty=10000
%\exhyphenpenalty=10000

\begin{document}
\thispagestyle{empty} % suppresses the page number
{\raggedleft Ian Joynes \\
P.O. Box: 1444 \\
34 Wolfe Ave. \\
Deep River, Ontario \\
K0J 1P0 \\ 
 }
\vspace{20pt}
January 16, 2014
\vspace{20pt}


To the Hiring Manager for Fluid Dynamics Research Engineer (PM2013-08),

I am a Master of Applied Science graduate from the Carleton University Mechanical Engineering program. Please accept this as my formal application for the fluid dynamics research engineer position within Coanda, as I believe that I could make a significant contribution to process flow modelling and design optimization projects currently underway.

My master's thesis focused on pollution source location and quantification with inverse dispersion modelling.  This project required me to develop my own code to model pollution transport, as well as master using both commercial and open source computational fluid dynamics packages, numerical optimization codes, and data visualization software.  I have also presented my work at both the 2011 and 2012 Air \& Waste Management Association's Annual Conference and Exposition.  From my attached university transcript, you will see that I have also excelled in numerical analysis, computational fluid dynamics and finite element analysis courses at both the undergraduate and graduate levels.

Currently, I am continuing my inverse dispersion modelling research as a research assistant at Carleton University.  Additionally, I have work experience with Atomic Energy of Canada Limited (AECL) during the summers of 2006 through 2008 as an engineering student. During this time I developed tooling to be used by NRU Reactor Operations staff, assisted with rolled joint qualification testing, performed materials testing and produced quality assurance documentation templates.

I believe the skills I have developed at Carleton University and AECL could make useful contributions to Coanda's flow modelling and design optimization projects. I can be contacted though e-mail at \href{mailto:ian@joynes.com}{ian@joynes.com} or by phone at 613-795-9171. I am looking forward to discussing with you how my skills could be used.\\
\\
\\
Sincerely, \\
\vspace{30pt} \\
Ian Joynes

\end{document}
